Merging merges, more or less

### 2015-04-09 2015mergingmerges/section/04-Invariants.tex
remove psis
proof of closure transitions

\subsubsection{Generation}
Figure~\ref{fig:inv:generation}.

@@

\subsubsection{Checking}
Figure~\ref{fig:inv:checking}.

@@

\subsubsection{Environment closure}
Figure~\ref{fig:inv:closure}.

@@

\subsubsection{Entire machine}
Figure~\ref{fig:inv:entire}.

First, the environment closure is computed, starting with the initial state of the machine having no available information.
Next, every state of the machine is checked to be valid against the environment closure.

>>>>

\subsection{Generation}
Figure~\ref{fig:inv:generation}.

@@

\subsection{Checking}
Figure~\ref{fig:inv:checking}.

@@

\subsection{Environment closure}
Figure~\ref{fig:inv:closure}.

@@

$$ \EnvMachine{m}{\Gamma} $$
The environment closure for an entire machine is computed by starting with the initial state of the machine having no available information.

\subsection{Entire machine}
Figure~\ref{fig:inv:entire}.

Every state of the machine is checked to be valid against the environment closure.

### 2015-04-09 2015mergingmerges/section/05-Proofs.tex
add conclusion
proof of closure transitions

\section{Proofs}
\label{s:Proofs}

@@

\paragraph{Lemma values:} 
for each state $u$ of $@merge@~a~b$, if either event set contain a @Value n@, then the machine's invariant set will contain @Value n@ at state $u$.
(Note that the converse is not true, as @Value n@ will appear in the invariant set, but neither event set for local @Out@s)

>>>>

%!TEX root = ../Main.tex
\section{Proofs}
\label{s:Proofs}

@@

The final requirement for correct fusion is the two machines to satisfy their invariants.
\begin{tabbing}
MMMMMMM \= MM \= \kill
$@oks@~a~b$
\> $:=$
\> $@acyclic@~a~b~\wedge~@distinct@~a~b$ \\
\> $\wedge$ \> $@ok@~a~\wedge~@ok@~b$ \\
\end{tabbing}

\subsection{Closure transitions}
The first lemma we require is to show that the environment closure computes the intersection of all transitions into a given state.

We would like to show that this holds for computing the closure for an entire machine:

\begin{tabbing}
MM \= MM \= MM \= \kill
$\forall...$ \\
\> \> $\EnvMachine{m}{\Gamma}$ \\
\> $\wedge$ \> $u~:_E~e~\in~\Gamma$ \\
\> $\implies$\> $\bigcap \{e'~|~n~\Rightarrow~u~\in~m$ \\
\>           \>         \> $\wedge~\CheckOutTransUP{\Gamma'}{n}{u}{e'} \}$ \\
\> $=$       \> $e$
\end{tabbing}

However this is not quite true, as the environment closure is only computed for reachable transitions.
We also need a weaker postcondition in order to perform induction over the closure environment.
We add the extra constraint that only transitions reachable from the pending state are considered.
We also take into account the intersection of the initial set and the pending set.

The actual lemma to prove, then, is:

\begin{tabbing}
MM \= MM \= MM \= \kill
$\forall...$ \\
\>          \> $\EnvGrow{\Gamma}{p}{\Gamma'}$ \\
\> $\wedge$ \> $u~:_E~e~\in~\Gamma'$ \\
\> $\implies$\> $\bigcap\{e'~|~n~\Rightarrow~u~\in~m$ \\
\>           \>         \> $\wedge~\CheckOutTransUP{\Gamma'}{n}{u}{e'}$ \\
\>           \>         \> $\wedge~@exists path from p to u@\}$ \\
\> $\cap$ \> $\bigcap\{e' ~|~ u~:_E~e'~\in~\Gamma \} $ \\
\> $\cap$ \> $\bigcap\{e' ~|~ u~:_E~e'~\in~p \} $ \\
\> $=$       \> $e$
\end{tabbing}

We can proceed by induction over the closure.

(CloComputed):
regardless of whether $s~=~u$ or not, we simply use the induction hypothesis; since $a~=~b$, removing $s$ from $p$ does not change the result, as $s~:_E~a$ is left in $\Gamma$.

(CloRemoveOut):
again, we just use the induction hypothesis;
$s$ is removed from $\Gamma$ but the intersection of $\Gamma$'s $s$ and $p$'s $s$ is inserted into $p$.

(CloTransitions):
if $s~=~u$, the intersection is not affected as it is moved from $p$ to $\Gamma$.
If $u$ is one of the transitions from $s$, it is already in the first part of the intersection, so adding it to $p$ will not change the intersection.

(CloFinished):
here, $p$ is empty and there is no path from any elements of $p$ to $u$, so neither the first nor the last intersections have any effect, and the result is just $\Gamma$.

\subsection{Values}
For each state $u$ of $@merge@~a~b$, if either event set contains a @Value n@, then the machine's invariant set will contain @Value n@ at state $u$.
(Note that the converse is not true, as @Value n@ will appear in the invariant set, but neither event set for local @Out@s)

\begin{tabbing}
MMMMMMM \= MM \= MM \= \kill
$\forall a~b.\ \forall u \in (@merge@~a~b).$
\\
\>
\> $@oks@~a~b$
\\
\> $\wedge$
\> $\EnvMachine{@merge@~a~b}{\Gamma}$
\\
\> $\wedge$
\> $u~:_E~e~\in~\Gamma$
\\
\> $\wedge$
\> $\Value{n}~\in~(u \cdot e_1~\cup~u \cdot e_2)$
\\
\> $\implies$
\> $\Value{n}~\in~e$
\end{tabbing}

Let $m~=~@merge@~a~b$.

We first apply rule (CloMachine) to the assumption.

$$
\EnvMachine{@merge@~a~b}{\Gamma}
\implies
\EnvGrow{\emptyset}{@initial@~m~:_E~\emptyset}{\Gamma}
$$

We now proceed by induction over the closure.

$$
\EnvGrow{\Gamma}{p}{\Gamma'}
$$

(CloComputed): by the induction hypothesis.
